Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-20 manuscript/manuscript.tex
Move exponential density shell to the appendix

\noindent $R$ is the mean Earth radius and $b$ is a constant
that determines the variability of the function: a low value of $b$
increases the maximum slope of the density function.
The analytical solution of the gravitational potential generated by a
spherical shell with a density functions as the one in equation
\ref{eq:density-exp} can be obtained by solving the equation
\ref{eq:shell-pot} as follows:

\iftwocol{
\begin{equation}
    \begin{split}
        V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r}
        Ab
        \Big[
        & (R_1^2 + 2R_1 b + 2b^2)e^{-\frac{R_1 - \Delta h}{b}} - \\
        & (R_2^2 + 2R_2 b + 2b^2)e^{-\frac{R_2 - \Delta h}{b}}
        \Big] + \\
        & \frac{4 \pi G}{3 r} C (R_2^3 - R_1^3).
    \end{split}
\label{eq:shell-pot-exp}
\end{equation}
}{
\begin{equation}
    V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r}
    Ab \, e^\frac{\Delta h}{b}
    \Big[
    (R_1^2 + 2R_1 b + 2b^2)e^{-\frac{R_1}{b}} -
    (R_2^2 + 2R_2 b + 2b^2)e^{-\frac{R_2}{b}}
    \Big] +
    \frac{4 \pi G}{3 r} C (R_2^3 - R_1^3).
\label{eq:shell-pot-exp}
\end{equation}
}

@@

>>>>

\noindent $R$ is the mean Earth radius and $b$ is a constant
that determines the variability of the function: a low value of $b$
increases the maximum slope of the density function.

@@

An exponential density function that assumes the values of $\rho_\text{out}$ and
$\rho_\text{in}$ on the shell's outer and inner surfaces, respectively, can be defined
as follows:

\begin{equation}
    \rho(r') = A e^{-(r' - R)/b} + C,
\label{eq:density-exp}
\end{equation}

\begin{equation}
    A = (\rho_\text{in} - \rho_\text{out})
        \left( e^{( R_2 - R_1 )/b} - 1 \right)^{-1},
\end{equation}

\begin{equation}
    C = \rho_\text{out} - A,
\end{equation}

\noindent $R$ is the mean Earth radius, and $b$ is a constant
that determines the variability of the function: a low value of $b$
increases the maximum slope of the density function.

The analytical solution of the gravitational potential generated by a
spherical shell with a density function given by equation
\ref{eq:density-exp} is

\iftwocol{
\begin{equation}
    \begin{split}
        V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r}
        Ab
        \Big[
        & (R_1^2 + 2R_1 b + 2b^2)e^{-\frac{R_1 - R}{b}} - \\
        & (R_2^2 + 2R_2 b + 2b^2)e^{-\frac{R_2 - R}{b}}
        \Big] + \\
        & \frac{4 \pi G}{3 r} C (R_2^3 - R_1^3).
    \end{split}
\label{eq:shell-pot-exp}
\end{equation}
}{
\begin{equation}
    V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r}
    Ab \, e^\frac{R}{b}
    \Big[
    (R_1^2 + 2R_1 b + 2b^2)e^{-\frac{R_1}{b}} -
    (R_2^2 + 2R_2 b + 2b^2)e^{-\frac{R_2}{b}}
    \Big] +
    \frac{4 \pi G}{3 r} C (R_2^3 - R_1^3).
\label{eq:shell-pot-exp}
\end{equation}
}
